---
title: "Understanding ANOVA"
author: "Kay Darko"
date: "December 1, 2019" "continued ob Dec 9th at African studies library"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an explanation of ANOVA in R.
ANOVA= One way Analysis of Variance
is used to analyze the relationship between one X variable(categorical/ factor with independent levels/groups)
and Y variable which continuous.
 
```
#Montag<-seq(from=2, to=8, length.out=4) 
#Dienstag<-Montag-2
#Mittwoch<-Montag*1.5
#cat_x<-as.factor(c(Montag,Dienstag,Mittwoch)) created a factor with eight levels instead of three

cat_x1=as.factor(c("Montag", "Dienstag","Mittwoch"))

mat1<-matrix(c(Montag,Dienstag, Mittwoch), nrow=4, ncol=3)
mat1a<-matrix(c(Montag,Dienstag, Mittwoch), nrow=3, byrow=T) #this what I want 3 x 4 matrix
mat1b<-matrix(c(Montag,Dienstag, Mittwoch), byrow=T)
mat1c<-matrix(c(Montag,Dienstag, Mittwoch))

organism<-c("Human","Mouse","Fruit Fly", "Roundworm","Yeast")
genomeSizeBP<-c(3000000000,3000000000,135600000,97000000,12100000)
estGeneCount<-c(30000,30000,13061,19099,6034) 
y<-rnorm(15,9.18,2.29)

y1<-rbinom(3, 10, 0.75)

y2<-rbinom(3,1,0.75)
y2a<-rbinom(3,2,0.75)
y2d<-rbinom(3,3,0.75)
#y2f<-rbinom(3,4,0.75)
#y2g<-rbinom(3,5,0.75)
#y2h<-rbinom(3,6,0.75)
df1<-data.frame(organism=organism,genomeSizeBP=genomeSizeBP,estGeneCount=estGeneCount)
str(y)

df2<-data.frame(explanatory_var=cat_x1, response_var=y)
df2_a<-data.frame(explanatory_var=cat_x1, response_var=y1)

Humans<-as.factor(c("baby", "toddler", "teenager"))
Try1<-as.
df3<-data.frame(Humans=Humans,)



library(ggplot2)
plot1<-ggplot(df2_a,aes(df2_a$explanatory_var, df2_a$response_var))
p1<-plot1+lab(title="Trial boxplot")

p2<-plot(df2_a$explanatory_var, df2_a$response_var)
p2
plot(Humans,y2h)

par(nrow(2))
boxplot(y, ylim=c(0,15), ylab="Amount of Rainfall", main="#Boxplot", las=1)
quantile(y, probs=c(0,0.25,0.5,0.75,1))


document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
